---
title: "My first Markdown Presentation"
author: "Francisco Javier Álvarez-Vargas"
date: "16/9/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
```
```{r}
library(pander)
library(plotly)
```

## DEVELOPING DATA PRODUCTS
### R Markdown Presentation & Plotly
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

### Review Criteria
The rubric contains the following two questions:

1. Is the presentation less than two months old?
2. Is it an interactive presentation, which appears to have been created with Plotly?


## Edgar Anderson's IRIS Data
Iris data set gives the measurements in [cm] of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are *Iris setosa*, *I. versicolor*, and *I. virginica*.

```{r iris}
pander(summary(iris), caption="Summary for iris database")
```

## Are there differences in petals length?
Let's look at this image, (and p-Value):
```{r}
plot_ly(iris, y = ~Petal.Length, color = ~Species, type = "box")
```
```{r}
(kruskal.test(Petal.Length ~ Species, data=iris))$p.value
```


## Are there differences in sepals length?
```{r}
plot_ly(iris, y = ~Sepal.Length, color = ~Species, type = "box")
```
```{r}
(kruskal.test(Sepal.Length ~ Species, data=iris))$p.value
```


## Is there a relationship between these two lengths?
```{r}
p <- ggplot(iris, aes(Sepal.Length, Petal.Length, 
            color=Species)) + 
     geom_point() +
     geom_smooth(method="lm")
ggplotly(p)
```

